\documentclass{screenplay}[2012/06/30]
\title{Bambi \& Ooh La La La\\`untitled'}
\author{HD}
\address{University College London\\+44 7305 576221\\hd@hashadar.com}
\begin{document}
\coverpage
\fadein
\intslug[day]{Student Centre}
Song starts: OOH LA LA LA 

LEAD 1 sits at a table and prepares to do some work. (00:00 - 00:10)

Sitting opposite and adjacent is LEAD 2. LEAD 1 looks at LEAD 2 who lifts their head and looks at him in the eyes. (When I turn my head, my eyes meet yours 00:10 - 00:15).

LEAD 2 puts their head down and resumes working, shortly followed by LEAD 1. (and once again, I'm just left staring at you 00:15 - 00:21).

LEAD 2 friends come over and they begin talking and laughing. LEAD 1 is focused on LEAD 2 laughing and smiling. (That smile is a bit too much for me, filled with an ease leaving me to burn. 00:21 - 00:27)

LEAD 1 stands to get some water, he smiles to himself as he fills his bottle. (I can't breathe when I see your eye smile 00:27 - 00:31)

LEAD 2's friends leave and she also stands to get some water with a vibrant energy (it seems like you know that's your charm 00:31 - 00:34) 

LEAD 1 sees LEAD 2 through the cafe window (yeah yeah yeah 00:34 - 00:35)

LEAD 1 has caught feelings (la la la la 00:35 - 00:37)

LEAD 2 catches LEAD 1 looking at them and smiles (your eyes are whispering to me 00:37 - 00:41)

LEAD 1 walks through the door as LEAD 2, opposite, approaches (la la la la 00:41 - 00:43)

LEAD 1 and LEAD 2, both looking at each other, approach each other (It's like they're asking me to approach you 00:43 - 00:46). Dancers move onstage in a similar fashion into formation.

\intslug{DANCE - EXO | OOH LA LA LA to 02:07} 
\end{document}